%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
      \textit{\small #3} & \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Viktor Sharha} \\ \vspace{6pt}
  {\small Computer Science student at the University of Edinburgh focused on AI automation, NLP, and full-stack systems.} \\ \vspace{4pt}

  \href{mailto:vsharha07@gmail.com}{\underline{vsharha07@gmail.com}} $|$
  \href{https://www.linkedin.com/in/vsharha/}{\underline{linkedin.com/in/vsharha}} $|$
  \href{https://github.com/vsharha/}{\underline{github.com/vsharha}} $|$
  \href{https://viktorsharha.com/}{\underline{viktorsharha.com}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Edinburgh}{Edinburgh, Scotland}
{BEng Computer Science}{Expected Graduation: May 2028}
% \resumeItemListStart
% \resumeItem{Introduction to Computation}
% \resumeItem{Introduction to Linear Algebra}
% \resumeItem{Fundamentals of Algebra and Calculus}
% \resumeItem{Object Oriented Programming}
% \resumeItem{Calculus and its Applications}
% \resumeItem{Cognitive Science}
% \resumeItemListEnd
\resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Python, JavaScript, Java, C++, Bash, SQL, HTML/CSS
        } \\
        \textbf{Frameworks}{: React, Next.js, Redux, Tailwind CSS, FastAPI} \\
        \textbf{Tools \& Platforms}{: Git, Linux, Docker, OpenAI API, Cloudflare} \\
        % \textbf{Specializations}{: Natural Language Processing (NLP), Optical Character Recognition (OCR), Data Pipelines, Full-Stack Web Development}
        %  \textbf{Developer Tools}{: GitHub, VS Code, PyCharm} \\
        %  \textbf{Libraries}{: Discord.py}
        }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{VDrive Chip, Key \& Diagnostics}{June 2025 -- Present}
{Technical Operations Specialist}{Edinburgh, Scotland}
\resumeItemListStart
\resumeItem{Led the setup of end-to-end business systems, implementing HMRC registration, banking, and accounting platforms to enable compliant service delivery.}
\resumeItem{Crafted brand identity and booking website with integrated scheduling across digital channels, streamlining customer intake}
\resumeItem{Restored 6+ months of financial history by engineering a custom data extraction tool, re-establishing accurate financial reporting}
\resumeItemListEnd

% \resumeSubheading
% {Standard Life}{June 2024 -- July 2024}
% {Career Ready Internship}{Edinburgh, Scotland}
% \resumeItemListStart
% \resumeSubheading
% {Standard Life}{June 2024 -- July 2024}
% {Career Ready Internship}{Edinburgh, Scotland}
% \resumeItemListStart
% \resumeItem{Designed and refined questions to drive a market research study}
% \resumeItem{Created data visualizations to highlight key trends for internal research}
% \resumeItem{Chose and recommended new content for a mobile app}
% % \resumeItem{Helped prepare and deliver a presentation of findings}
% \resumeItem{Presented research insights directly to a group of potential users}
% \resumeItemListEnd

\resumeSubHeadingListEnd


% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\section{Awards \& Honors}
\resumeSubHeadingListStart
\resumeSubheading
{First Place, OpenEuler Challenge}{October 2025}
{Samantha OS Assistant}{Edinburgh, Scotland}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Personal Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Samantha OS Assistant} $|$ \emph{Python, OpenAI API, openEuler Linux, Natural Language Processing}}{October 2025}{A conversational AI terminal assistant that translates natural language into system commands}
\resumeItemListStart
\resumeItem{Engineered a command-line interface (CLI) assistant that maps conversational requests to file, search, and diagnostic workflows via Python agents and the OpenAI API, streamlining day-to-day system maintenance.}
\resumeItem{Built a modular tool framework with extensible base classes for web fetches, media handling, and directory analysis, enabling rapid addition of new capabilities.}
\resumeItem{Enabled self-correction with conversation memory that logs failures, retries alternative strategies, and preserves context across multi-turn tasks to maintain reliability.}
% \resumeItem{Added a safety layer that previews commands and requires confirmations for risky actions to prevent destructive errors.}
\resumeItemListEnd


\resumeProjectHeading
{\textbf{\href{https://wordle-international.netlify.app}{\underline{Wordle International}}} $|$ \emph{React, Redux Toolkit, Tailwind CSS, Vite}}{September -- October 2025}{Multilingual Wordle with configurable modes and API-backed words}
\resumeItemListStart
\resumeItem{Shipped configurable game modes with React and Redux Toolkit so players can adjust word length and attempts for unlimited practice.}
\resumeItem{Built a FastAPI random-word service supporting 15 languages; implemented an auto-adjusting on-screen keyboard with locale-aware input.}
\resumeItem{Designed a responsive Tailwind UI for mobile and desktop with an adaptive grid and touch-friendly controls.}
\resumeItem{Managed guess validation and keyboard state with Redux Toolkit, adding an offline fallback when the API is unavailable; added URL parameters using React Router.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/vsharha/Words-FrequencyPOS}{\underline{Words-FrequencyPOS}}} $|$ \emph{Python, Bash, Data Pipelines}}{September 2025}{Cross-lingual frequency + POS dataset pipeline powering language-learning and NLP research}
\resumeItemListStart
\resumeItem{Delivered an automated extraction-transformation-load (ETL) pipeline that merges multilingual word-frequency and part-of-speech (POS) datasets with Python and Bash to support cross-lingual analysis.}
\resumeItem{Linked frequency data with POS and morphology metadata to answer POS-specific vocabulary queries for linguistics and natural language processing (NLP) studies.}
\resumeItem{Automated end-to-end runs with command-line scripts and environment-based configuration, enforcing idempotent downloads and resume-safe processing.}
\resumeItem{Produced reproducible, versioned artifacts ready for batch processing and programmatic integration.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AI Expense Pipeline} $|$ \emph{Python, AI provider APIs}}{July -- August 2025}{An automated invoice and receipt processing pipeline with configurable AI-driven extraction}
\resumeItemListStart
\resumeItem{Constructed a modular pipeline that ingests PDF invoices and receipts, normalizes inputs with optical character recognition (OCR), and extracts structured expense data through AI-generated prompts to speed bookkeeping.}
\resumeItem{Designed YAML-driven processing passes with carry-forward fields, skip logic, and post-processing rules (joins, length limits, date bounds) to keep outputs consistent.}
\resumeItem{Orchestrated multiple AI providers with structured logging and tests, mapping responses into typed fields for reliable auditing.}
\resumeItemListEnd
% \resumeProjectHeading
% {\textbf{\href{https://github.com/vsharha/Java-Banking-System}{\underline{Banking System}}} $|$ \emph{Java}}{January 2025}{A banking application with a command-line interface}
% \resumeItemListStart
% \resumeItem{Implemented account registration, balance operations, and timestamped transaction history}
% \resumeItem{Applied appropriate data structures and object-oriented design patterns to ensure correctness, maintainability, and
%   extensibility}
% \resumeItemListEnd
% \resumeProjectHeading
%   {\textbf{\href{https://viktorsharha.com/}{\underline{Portfolio}}} $|$ \emph{JavaScript, HTML/CSS}}{August 2024}{A personal portfolio website to showcase some of my personal projects}
%   \resumeItemListStart
% \resumeItem{Set up website hosting and a custom domain using Cloudflare}
% \resumeItem{Implemented carousel functionality using JavaScript}
% \resumeItem{Leveraged media queries in CSS to achieve responsive design for an optimal user experience on different devices}
% \resumeItemListEnd

% \resumeProjectHeading
% {\textbf{\href{https://github.com/vsharha/HangmanBot/}{\underline{HangmanBot}}} $|$ \emph{Python, Discord.py}}{September 2023}{A Discord bot to let users play hangman together}
% \resumeItemListStart
% \resumeItem{Designed a bot to enhance user interaction across multiple Discord communities}
% \resumeItem{Implemented a variety of commands to facilitate hangman games}
% \resumeItem{Gathered and incorporated user feedback to fine-tune features}
% \resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}